---
title: "Developing Data Products - Slide Pitch"
author: "b m g"
date: "6/26/2017"
transition: rotate
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Objectives

* Build a shiny application with documentation 
      + showing use of user input widgets and 
      + calculations on server side based on user input values 
* Host the application on a shiny server 
* Publish a set of 5 slides to pitch the applciation
* The data set "iris" from R is used. See references.
      + The source code for the project can be found in github public repository
      +  https://github.com/b-mc-g/developing_data_products_w4/tree/master
      + Presentation data can be found using gh.pages link in browser here
      + http://b-mc-g.github.io/developing_data_products_w4/index.html
      
## Application
* The application uses the "iris" data preloaded with R
* On right of the screen
      + Petal and Sepal width and length are plotted on 4 graphs
* On left of screen
      + Four sliders allow the values to be set
      + These could be used to enter actual measurement
* Bottom Left there is a Predict Species button
      + This allows the set slider values to be entered
      + into a random forest model geberated using the "iris" data
      + the predicted species is returned and show in table form to the user
      + values are shown as decimals that add up to 1


## Example Graph used in the application

```{r, echo = FALSE, message=FALSE}
library(ggplot2)
data("iris")
```
* Sepal Length probalilty densities for the 3 Species
* The app allows the user to set measurement values using  sliders
```{r, echo = FALSE}
ggplot(iris, aes(x = Sepal.Length,
                 group = Species,
                 fill = as.factor(Species))) + 
      geom_density(position = "identity", alpha = 0.5) +
      scale_fill_discrete(name = "Species") +
      theme_bw() +
      xlab("Sepal Length") +
      geom_vline(xintercept = 7,
                 color = "blue",
                 size = 1.5) +
      scale_x_continuous(limits = c(round(min(iris$Sepal.Length) / 2, 1),
                                    round(max(iris$Sepal.Length) * 1.25, 1)))
```

## Additional References

- https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/iris.html
- https://shiny.rstudio.com/tutorial/
- https://shiny.rstudio.com/articles/
- https://shiny.rstudio.com/gallery/


